\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=2cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}
\usepackage{fontawesome5}
\usepackage{titlesec}

% Define colors
\definecolor{primary}{RGB}{50,50,50}
\definecolor{accent}{RGB}{0,70,140}

% Configure hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=accent,
    urlcolor=accent
}

% Configure section titles
\titleformat{\section}
    {\Large\bfseries\color{accent}}
    {}{0em}
    {}[\titlerule]
\titlespacing*{\section}
    {0pt}{12pt}{8pt}

% Personal Info Command
\newcommand{\personalinfo}[1]{{\large #1}}

% Header Command
\newcommand{\cvheader}[1]{{\LARGE\bfseries\color{primary} #1}}

% Job title command with date below
\newcommand{\jobtitle}[2]{
    \noindent\textbf{#1}\\
    \textit{#2}\par\vspace{0.5em}
}

\begin{document}

% Header with more spacing
\begin{center}
\cvheader{Jorge Daniel Gonzalez}
\vspace{1.5em}  % Increased spacing
{\large\color{accent}\textbf{Software Developer}}
\end{center}

\vspace{1.5em}  % Increased spacing after title

% Contact information
\begin{center}
\begin{tabular}{r l}
\faEnvelope & \href{mailto:jorgedaniel29.jg@gmail.com}{jorgedaniel29.jg@gmail.com} \\[0.3em]
\faPhone & +54 9 11 3020 8941 \\[0.3em]
\faMapMarker & Dr. Gabriel Ardoino 490, Ramos Mejía, Buenos Aires \\[0.3em]
\faLinkedin & \href{https://www.linkedin.com/in/jorge-daniel-gonzalez-8783a2112/}{jorge-daniel-gonzalez} \\[0.3em]
\faGithub & \href{https://github.com/JorgeDaniel29}{JorgeDaniel29}
\end{tabular}
\end{center}

\vspace{1em}

\section{Professional Summary}
I am a software developer specializing in Android with over 9 years of experience, currently working as a Software Technical Lead at Mercado Libre. I possess a comprehensive understanding of Android development lifecycles, frameworks, architecture components, mobile analytics, and agile methodologies.

I have a strong focus on software architecture, especially Clean Architecture and MVVM, combining technical excellence with leadership skills to guide teams and define quality standards. I am dedicated to implementing new technologies to produce scalable, maintainable, innovative, and robust applications within the Mercado Pago ecosystem.

As an enthusiast of computer science, algorithms, and programming, I continuously expand my knowledge through research, technical literature, and staying current with industry trends. I am passionate about building efficient solutions with real impact on user experience, constantly seeking challenges that drive professional growth and add value to high-impact projects.

\section{Professional Experience}

\jobtitle{Mercado Libre — Software Technical Lead / Sr Android Developer}{May 2019 – Present}
\begin{itemize}[leftmargin=*]
    \item Development and maintenance of features for the Mercado Pago checkout and other key libraries of the ecosystem (card art, card enrollment, security code encrypted, Payment link).
    \item Team technical leadership, architecture definition, mentoring, code review, and technical planning.
    \item Solid knowledge in clean architecture (MVVM, layer separation by responsibility, use cases), coroutines, Retrofit 2, Picasso, Koin and Service locator for dependency injection, android services, unit testing, CI/CD.
    \item Integrations with tools like Bugsnag for tracking bugs, Kibana for tracking backend logs, and Alation for business metrics.
\end{itemize}

\jobtitle{IguanaFix — Android Developer}{March 2018 – April 2019}
\begin{itemize}[leftmargin=*]
    \item Development and maintenance of the IguanaFix customer app.
    \item Stack: Kotlin, RxJava, Retrofit 2, Firebase (Crashlytics, Analytics, Cloud-messaging), Room, ViewModel, Glide, Butter Knife, GoogleMaps API, Fresco, Picasso.
    \item Implementation of Android Architecture Components (LiveData, ViewModel, Room), MVVM pattern, and Material Design.
\end{itemize}

\jobtitle{Fusap — Java Mobile Junior Programmer}{April 2016 – February 2018}
\begin{itemize}[leftmargin=*]
    \item Development of Android apps for private companies.
    \item Technologies: Firebase, GoogleMaps API, Volley, EventBus, Glide.
\end{itemize}

\jobtitle{Codere Bingo — Electronics Technician}{March 2015 – March 2016}
\begin{itemize}[leftmargin=*]
    \item Maintenance, cleaning, and diagnosis of electronic gaming machines.
\end{itemize}

\jobtitle{OSED Entidad Educativa — Customer Service}{December 2011 – January 2014}
\begin{itemize}[leftmargin=*]
    \item Customer service, sales, administration, opening and closing of the premises.
\end{itemize}

\jobtitle{Freelancer — Electronics Technician}{2008 – 2010}
\begin{itemize}[leftmargin=*]
    \item Assembly and soldering of electronic boards at the request of private clients.
\end{itemize}

\section{Education}

\textbf{Computer Science Engineering}
\begin{itemize}[leftmargin=*]
    \item Universidad Nacional de La Matanza, Buenos Aires (2014 – 2019)
    \item Advanced university training in software development and systems architecture, completed up to the third year
\end{itemize}

\textbf{Electronics Technician}
\begin{itemize}[leftmargin=*]
    \item E.E.T. Nº 8, Morón, Buenos Aires (2006 – 2010)
\end{itemize}

\textbf{Additional Certifications}
\begin{itemize}[leftmargin=*]
    \item PC Repair and Assembly Technician (2010)
    \item Cell Phone Repair Technician (2010)
    \item Work Orientation and Induction Program (POI)
    \begin{itemize}
        \item Computing
        \item Occupational Training Project
        \item Workplace Health and Safety
        \item Labor Rights
    \end{itemize}
\end{itemize}

\section{Technical Skills}

\begin{itemize}[leftmargin=*]
    \item \textbf{Programming Languages:} Kotlin, Java, C
    \item \textbf{Tools:} Git, Retrofit, Koin, Firebase, Room, Glide, Picasso
    \item \textbf{Methodologies:} Scrum, Clean Architecture, MVVM, CI/CD, Unit Testing
    \item \textbf{Soft Skills:} Effective Communication, Teamwork, Proactivity, Results-oriented
    \item \textbf{Languages:} Spanish (Native), English (Basic, in training)
\end{itemize}

\end{document} 